Challenges to the Two-Infall Scenario by Large Stellar Age Catalogs

### 2025-12-15 src/tex/ms.tex
Manuscript updates for referee report

% For TeXworks
% \makeatletter
% \declare@file@substitution{revtex4-1.cls}{revtex4-2.cls}
% \makeatother

% Define document class
\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex701}

% \usepackage{showyourwork}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{xspace}
% Dropped capital
\usepackage{lettrine}

@@

The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the $\alpha$-bimodality in the MW. The basic premise is that the rate of gas accretion onto the disk occurs in two bursts. The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas abundance to evolve between the high- and low-$\alpha$ sequences while producing few stars. 
% The infall timescale for the low-$\alpha$ disk can vary with radius to produce inside-out disk growth and a radial metallicity gradient \citep{romano_mass_2000}.
% The initial model of 
\added{\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and}
subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}. Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}, \added{and additional episodes of gas accretion \citep{spitoni_beyond_2023,palla_mapping_2024}}. Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.

\added{While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow. The presence of mass-loaded outflows in MW-like galaxies is heavily debated \citep[see discussion in][]{johnson_milky_2025}, but even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.} 
By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,weinberg_equilibrium_2017,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}. 
% \citet{weinberg_equilibrium_2017} showed that the equilibrium metallicity is primarily set by the yields and the outflow mass-loading factor; proportionally raising or lowering both may affect the time-dependence of abundance evolution but not the end-point. 
This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant. The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of varying the yield scale on two-infall scenario predictions. Varying the yield scale while maintaining an evolutionary end point consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.

@@

The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. 
However, 
% the current body of evidence suggests that many of the stars that make up the wings of the local metallicity distribution originate from elsewhere in the Galaxy. \citet{sellwood_radial_2002} first showed that transient spiral perturbations can induce large changes in the guiding radius of a star without kinematic heating, and 
it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{sellwood_radial_2002,schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}. 
A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth (e.g., \citealt{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}; \added{but see also \citealt{johnson_stellar_2021,dubay_galactic_2024}}). In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history.
% (although the models of \citealt{johnson_stellar_2021} and \citealt{dubay_galactic_2024} failed to produce an $\alpha$-bimodality).
Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii. 
If the effect of radial migration is significant, then the local $\alpha$-bimodality could be explained without dramatic changes to the local gas abundance over time.

@@

We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}. The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}. We set up a disk spanning $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$. We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$. \added{We adopt a \citet{kroupa_variation_2001} initial mass function (IMF).} Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling. Stellar populations migrate between zones, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones, which couples the enrichment in nearby rings. We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.

We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, and the stellar migration prescription in Section \ref{sec:migration}. We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}. Table \ref{tab:parameters} summarizes the model parameters and their fiducial values.

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Value or Range} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        R_{\rm gal}         & $[0,20]\kpc$  & \ref{sec:methods}     & Galactocentric radius \\
        \delta R_{\rm gal}  & $0.1\kpc$     & \ref{sec:methods}     & Radial zone width \\
        R_{\rm SF}          & $15.5\kpc$    & \ref{sec:methods}     & Maximum radius of star formation \\
        t_{\rm final}       & $13.2\Gyr$    & \ref{sec:methods}     & Disk lifetime \\
        \Delta t            & $10\Myr$      & \ref{sec:methods}     & Time-step size \\
        n                   & 8             & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
        \dot M_r            & continuous    & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
        y/Z_\odot           & $[1,3]$       & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
        N_{\rm Ia}/M_\star  & $[1.55,3.57]\times10^{-3}\Msun^{-1}$  & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \\
        f_{\rm Ia}(t)       & Equations \ref{eq:plateau-dtd}, \ref{eq:powerlaw-dtd}     & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        t_{\rm Ia}          & $40\Myr$  & \ref{sec:yields}          & Minimum SN Ia delay time \\
        \eta_\odot          & $[0.2,2.4]$   & \ref{sec:outflows}    & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta              & $5.0\kpc$     & \ref{sec:outflows}    & Exponential outflow scale radius \\
        \tau_\star          & Equation \ref{eq:sf-law}              & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
        k                   & 1.5           & \ref{sec:sf-law}      & Star formation law exponent \citep{kennicutt_global_1998} \\
        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
        f_\Sigma(R_\odot)   & $[0.12, 0.5]$     & \ref{sec:sfh}     & Local thick/thin disk surface density ratio \\
        R_1                 & $2.0\kpc$         & \ref{sec:sfh}     & Thick disk scale radius \\
        R_2                 & $2.5\kpc$         & \ref{sec:sfh}     & Thin disk scale radius \\
        \mathXH_{\rm CGM}   & $(-\infty,-0.5]$  & \ref{sec:sfh}     & Metallicity of accreted gas \\
        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
        \tau_1              & $1\Gyr$       & \ref{sec:sfh}         & Timescale of the first infall epoch \\
        \tau_2(R_\odot)     & $15\Gyr$      & \ref{sec:sfh}         & Timescale of the second infall epoch at the Solar annulus \\
        R_{\tau_2}          & $7\kpc$       & \ref{sec:sfh}         & Exponential scale radius of the second infall timescale \\
        t_{\rm max}         & $4.2\Gyr$     & \ref{sec:sfh}         & Time of maximum gas infall (onset of second infall) \\
        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
        \sigma_{\rm RM8}    & $[2.68,5.0]\kpc$  & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
        z                   & $[-3,3]\kpc$      & \ref{sec:migration}   & Distance from Galactic midplane at present day \\
        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & \ref{sec:migration} & Disk scale height \\
    \enddata
\end{deluxetable*}

@@

The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models. \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$\footnote{
    In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$. We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
}\textemdash in other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun. However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed AMR. Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted an integrated SN Ia rate which is high compared to the measurement of \citet{maoz_star_2017}.

We therefore investigate yield sets at multiple scales. The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$\footnote{
    We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$. We note that for this empirical scaling, choosing different Solar abundances \citep[e.g.,][]{magg_observational_2022} would lead us to change the yields proportionally, so that our GCE model predictions in Solar-scaled abundances would actually be unchanged.
}, because we assume that all O is produced by CCSNe. For Fe, the CCSN yield is set by the \aFe ``plateau'' at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}. We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$. Our yield sets are presented in Table \ref{tab:yields}. We consider \yZ{1} representative of the empirical yield scale, whereas \yZ{2-3} span a range of theoretical predictions.

The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is set so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$. For \yZ{3}, the combined Fe yield of CCSNe and SNe Ia matches the Solar yield scale: $(y_{\rm Fe}^{\rm Ia}+y_{\rm Fe}^{\rm CC})/Z_{\rm Fe,\odot}=y/Z_\odot$; for \yZ{1} and \yZ{2}, we enhance $y_{\rm Fe}^{\rm Ia}$ by a factor of 30\% and 10\%, respectively, to reach the desired end-point. The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
\begin{equation}
    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}},
    \label{eq:snia-rate}
\end{equation}
for each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}. The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.

Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate per unit mass of star formation is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_{\rm Ia}}^{t_{\rm final}} f_{\rm Ia}(t') dt'}, & t \ge t_{\rm Ia} \\
        0 & t < t_{\rm Ia},
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_{\rm Ia}=40\,{\rm Myr}$ is the minimum SN Ia delay time, $t_{\rm final}=13.2\,{\rm Gyr}$ is our assumed lifetime of the Galactic disk, and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We also explore a simple power-law DTD,
\begin{equation}
    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1}.
    \label{eq:powerlaw-dtd}
\end{equation}
Equation \ref{eq:powerlaw-dtd} is consistent with SN Ia surveys \citep[e.g.,][]{maoz_star_2017} and results in more prompt Fe production.
We discuss the implications of using the power-law DTD in Section \ref{sec:abundance-distributions}.

@@

In this work, we have highlighted a few predictions of the two-infall scenario and compared against trends from large stellar age catalogs. We have explored a wide range of parameter space, but our investigation is not intended to be exhaustive. In this section, we discuss other parameters explored by previous studies as well as further extensions to the two-infall model.

>>>>

\documentclass[trackchanges,twocolumn,twocolappendix,linenumbers]{aastex701}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\let\tablenum\relax
\usepackage{siunitx}
\usepackage{xspace}
% Dropped capital
\usepackage{lettrine}

@@

The two-infall scenario was first proposed by \citet{chiappini_chemical_1997} to explain the origin of the $\alpha$-bimodality in the MW. The basic premise is that the rate of gas accretion onto the disk occurs in two bursts. The relatively low infall rate between the two bursts causes star formation to slow down, allowing the gas \added{metallicity} to evolve between the high- and low-$\alpha$ sequences while producing few stars. \added{\citet{chiappini_chemical_1997} successfully reproduced the Solar neighborhood abundance data available at the time, and} subsequent studies refined the two-infall scenario to reproduce abundance data across the disk \citep[e.g.,][]{chiappini_abundance_2001,chiappini_oxygen_2003}, as well as the local surface densities of stars and gas and the local star formation and supernova rates \citep[e.g.,][]{romano_mass_2000,spitoni_galactic_2020,spitoni_remind_2024}. Others have explored the SN Ia delay-time distribution \citep{matteucci_effect_2009,palicio_analytic_2023}, galactic fountains \citep{spitoni_effects_2009}, radial gas flows \citep{spitoni_effects_2011,palla_chemical_2020}, variations in the star formation efficiency \citep{spitoni_effects_2011,palla_chemical_2020}, radial stellar migration \citep{spitoni_effect_2015,palla_mgfe_2022}, azimuthal abundance variations \citep{spitoni_2d_2019}, pre-enriched gas infall \citep{palla_chemical_2020,spitoni_remind_2024}, \added{and additional episodes of gas accretion \citep{spitoni_beyond_2023,palla_mapping_2024}}. Most recently, \citet{hegedus_reconstructing_2025} constrained the infall timescales using chemical abundances for $\sim400,000$ stars from the 19th data release of the Sloan Digital Sky Survey \citep[SDSS;][]{sdss_collaboration_nineteenth_2025}.

\added{While previous studies have explored a large parameter space, most have assumed that the Galactic disk never had a substantial outflow. The presence of mass-loaded outflows in MW-like galaxies is heavily debated \citep[see discussion in][]{johnson_milky_2025}, but even if the MW is not currently ejecting a substantial outflow, it may have done so in the past.} By neglecting Galactic outflows, previous studies of the two-infall scenario have been constrained in their choice of nucleosynthetic yields \citep{francois_evolution_2004} because of the yield--outflow degeneracy \citep[e.g.,][]{hartwick_chemical_1976,weinberg_equilibrium_2017,cooke_primordial_2022,johnson_dwarf_2023,sandford_strong_2024}. This degeneracy prohibits direct estimates of the yields from GCE models unless the effect of outflows is assumed to be insignificant. The predicted yields from CCSN models can vary substantially depending on the choice of initial mass function \citep{vincenzo_modern_2016} and the physics of black hole formation \citep{griffith_impact_2021}, yet few studies have investigated the effect of varying the yield scale on two-infall scenario predictions. Varying the yield scale while maintaining an evolutionary end point consistent with observations is straightforwardly achieved with simultaneous variations in the strength of outflows.

@@

The two-infall scenario reproduces the full distribution of stellar abundances in the Solar neighborhood through a single, continuous evolutionary track. However, it is now understood that the stars that make up the Solar neighborhood are drawn from a wide range of birth radii \citep[e.g.,][]{sellwood_radial_2002,schonrich_chemical_2009,frankel_measuring_2018,lian_quantifying_2022,lehmann_probing_2024}. 
A number of GCE studies have reproduced the $\alpha$-bimdodality using a combination of radial migration and smooth, inside-out galaxy growth (e.g., \citealt{schonrich_chemical_2009,kubryk_evolution_2015,sharma_chemical_2021,chen_chemical_2023,prantzos_origin_2023}; \added{but see also \citealt{johnson_stellar_2021,dubay_galactic_2024}}). In this scenario, the local high-$\alpha$ population originates from the inner Galaxy, where the star formation rate peaked early in its history. Figure \ref{fig:smooth-vs-twoinfall} contrasts the chemical evolution track for the Solar neighborhood predicted by a two-infall model against tracks from the smooth SFH model of \citet{johnson_stellar_2021} at three different radii. 
If the effect of radial migration is significant, then the local $\alpha$-bimodality could be explained without dramatic changes to the local gas abundance over time.

@@

We run multi-zone GCE models using the Versatile Integrator for Chemical Evolution \citep[{\tt VICE};][]{johnson_impact_2020}. \added{We wish to both approximate the Milky Way in gas and stellar density, present-day metallicity, and stellar abundance patterns, and to be able to tune parameters to help the two-infall scenario better match the observations and to reproduce the work of previous two-infall studies \citep[e.g.,][]{spitoni_galactic_2019,spitoni_apogee_2021,spitoni_remind_2024,palla_chemical_2020}.}

The basic format of our models follows \citet{johnson_stellar_2021} and \citet{dubay_galactic_2024}. We set up a disk spanning $0\leq R_{\rm gal}<20\kpc$ that is divided into concentric rings of width $\delta R_{\rm gal}=100\,{\rm pc}$. We use a time-step of $\Delta t=10\,{\rm Myr}$, $n=8$ stellar populations per time-step per ring, and we run our models to a final time of $t_{\rm final}=13.2\,{\rm Gyr}$. \added{We adopt a \citet{kroupa_variation_2001} initial mass function (IMF).} Within each ring, chemical evolution proceeds according to a conventional one-zone GCE model with instantaneous mixing and continuous recycling. Stellar populations migrate between zones, allowing the long-lived progenitors of SNe Ia to enrich areas of the Galaxy outside of their birth zones, which couples the enrichment in nearby rings. We inhibit star formation past $R_{\rm gal}>15.5\kpc$, so stars in the outer 4.5 kpc of the model disk represent a purely migrated population.

We discuss our assumptions about the nucleosynthetic yields in Section \ref{sec:yields}, the outflow prescription in Section \ref{sec:outflows}, the star formation law in Section \ref{sec:sf-law}, the gas supply equation in Section \ref{sec:sfh}, \added{the infall parameters in Section \ref{sec:infall-parameters}, the enrichment of the accreted gas in Section \ref{sec:cgm-enrichment},} and the stellar migration prescription in Section \ref{sec:migration}. We do not incorporate radial gas flows between the different zones, but we discuss their potential implications in Section \ref{sec:radial-flows}. Table \ref{tab:parameters} summarizes the model parameters and their fiducial values.

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Value or Range} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        R_{\rm gal}         & $[0,20]\kpc$  & \ref{sec:methods}     & Galactocentric radius \\
        \delta R_{\rm gal}  & $0.1\kpc$     & \ref{sec:methods}     & Radial zone width \\
        R_{\rm SF}          & $15.5\kpc$    & \ref{sec:methods}     & Maximum radius of star formation \\
        t_{\rm final}       & $13.2\Gyr$    & \ref{sec:methods}     & Disk lifetime \\
        \Delta t            & $10\Myr$      & \ref{sec:methods}     & Time-step size \\
        n                   & 8             & \ref{sec:methods}     & Number of stellar populations formed per ring per timestep \\
        \dot M_r            & continuous    & \ref{sec:methods}     & Recycling rate \citep[][Equation 2]{johnson_impact_2020} \\
        {\rm IMF}           & \citet{kroupa_variation_2001} & \ref{sec:methods} & Initial stellar mass function \\
        y/Z_\odot           & $[1,3]$       & \ref{sec:yields}      & Scale of nucleosynthetic yields (see Table \ref{tab:yields}) \\
        N_{\rm Ia}/M_\star  & $[1.55,3.57]\times10^{-3}\Msun^{-1}$  & \ref{sec:yields}  & SNe Ia per unit mass of stars formed \\
        f_{\rm Ia}(t)       & Equations \ref{eq:plateau-dtd}, \ref{eq:powerlaw-dtd}     & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        t_{\rm Ia}          & $40\Myr$  & \ref{sec:yields}          & Minimum SN Ia delay time \\
        \eta_\odot          & $[0.2,2.4]$   & \ref{sec:outflows}    & Outflow mass-loading factor at $R_\odot$ ($\eta\equiv\dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta              & $5.0\kpc$     & \ref{sec:outflows}    & Exponential outflow scale radius \\
        \tau_\star          & Equation \ref{eq:sf-law}              & \ref{sec:sf-law}      & Star formation efficiency timescale ($\tau_\star\equiv\Sigma_g/\dot\Sigma_\star$) \\
        k                   & 1.5           & \ref{sec:sf-law}      & Star formation law exponent \citep{kennicutt_global_1998} \\
        M_{\rm \star,tot}   & $5.17\times 10^{10}\Msun$     & \ref{sec:sfh} & Total stellar mass of the disk \citep{licquia_improved_2015} \\
        f_\Sigma(R_\odot)   & $[0.12, 0.5]$     & \ref{sec:sfh}     & Local thick/thin disk surface density ratio \\
        R_1                 & $2.0\kpc$         & \ref{sec:sfh}     & Thick disk scale radius \\
        R_2                 & $2.5\kpc$         & \ref{sec:sfh}     & Thin disk scale radius \\
        f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate} & \ref{sec:sfh} & Time-dependence of the gas accretion rate \\
        \tau_1              & $1\Gyr$       & \ref{sec:infall-parameters}         & Timescale of the first infall epoch \\
        \tau_2(R_\odot)     & $15\Gyr$      & \ref{sec:infall-parameters}         & Timescale of the second infall epoch at the Solar annulus \\
        R_{\tau_2}          & $7\kpc$       & \ref{sec:sfh}         & Exponential scale radius of the second infall timescale \\
        t_{\rm max}         & $[3.2,4.2]\Gyr$     & \ref{sec:infall-parameters}         & Time of maximum gas infall (onset of second infall) \\
        \mathXH_{\rm CGM}   & $(-\infty,-0.5]$  & \ref{sec:cgm-enrichment}     & Metallicity of accreted gas \\
        \sigma_{\rm RM}(\tau,R_{\rm form})  & Equation \ref{eq:radial-migration}    & \ref{sec:migration} & Width of Gaussian controlling radial migration distance \\
        \sigma_{\rm RM8}    & $[2.68,5.0]\kpc$  & \ref{sec:migration}   & Radial migration strength (width of $\sigma_{\rm RM}$ for $\tau=8\Gyr$) \\
        z                   & $[-3,3]\kpc$      & \ref{sec:migration}   & Distance from Galactic midplane at present day \\
        h_z(\tau,R_{\rm final}) & Equation \ref{eq:scale-height}    & \ref{sec:migration} & Disk scale height \\
    \enddata
\end{deluxetable*}

@@

The population-averaged nucleosynthetic yields of CCSNe, $y_{\rm X}^{\rm CC}$, are uncertain to a degree that is significant for chemical evolution models. \citet{weinberg_scale_2024} used a measurement of the mean Fe yield of CC SNe by \citet{rodriguez_iron_2023} and the plateau in stellar \aFe abundances at low metallicity to infer population-averaged yields of $y/Z_\odot\approx1$.\footnote{
    In this work, we will use the $y/Z_\odot$ notation to refer to the scale set by the massive star $\alpha$-element yields; i.e., $y_{\alpha}^{\rm CC}/Z_{\alpha,\odot}$. We also clarify that these yields refer to the net metal production by stellar populations; the return of previously produced metals in the envelopes of dying stars is handled separately by {\tt VICE}.
} In other words, for every $1\Msun$ of stars formed, massive stars release a quantity of newly-synthesized $\alpha$-elements (e.g., O or Mg) equal to their mass fraction in the Sun. However, \citet{johnson_milky_2025} found that their GCE models with this yield scale approach present-day abundances too slowly to match the observed AMR. Previous multi-zone models using {\tt VICE} \citep[e.g.,][]{johnson_stellar_2021,dubay_galactic_2024} adopted higher yields ($y/Z_\odot\approx2.6$) based on \citet{chieffi_explosive_2004} and \citet{limongi_nucleosynthesis_2006}; however, in order to produce a realistic evolution of [O/Fe], those studies adopted a \added{high} integrated SN Ia rate compared to the measurement of \citet{maoz_star_2017}.

We therefore investigate yield sets at multiple scales. The CCSN yield of O is directly set by the Solar scale, $y_{\rm O}^{\rm CC}=(y/Z_\odot)Z_{\rm O,\odot}$\footnote{
    We adopt the \citet{asplund_chemical_2009} Solar abundances: $Z_{\rm O,\odot}=5.72\times10^{-3}$ and $Z_{\rm Fe,\odot}=1.29\times10^{-3}$. We note that for this empirical scaling, choosing different Solar abundances \citep[e.g.,][]{magg_observational_2022} would lead us to change the yields proportionally, so that our GCE model predictions in Solar-scaled abundances would actually be unchanged.
}, because we assume that all O is produced by CCSNe. For Fe, the CCSN yield is set by the \aFe plateau at low metallicity, $\mathOFe_{\rm CC}$, such that $y_{\rm Fe}^{\rm CC}=(y/Z_\odot) Z_{\rm Fe,\odot} 10^{-\mathOFe_{\rm CC}}$ \citep[for further discussion on the empirical yield scale and the CCSN plateau, see][]{weinberg_scale_2024}. We set the plateau at $\mathOFe_{\rm CC}=+0.45$, which corresponds to an Fe yield from CCSNe of $y_{\rm Fe}^{\rm CC}=4.58\times10^{-4}(y/Z_\odot)$. Our yield sets are presented in Table \ref{tab:yields}. We consider \yZ{1} representative of the empirical yield scale, whereas \yZ{2-3} span a range of theoretical predictions.

The SN Ia yield of Fe, $y_{\rm Fe}^{\rm Ia}$, is \added{calibrated} so that our models reach $\mathOFe\approx0.0$ by $t=13.2\,{\rm Gyr}$. The fifth row of Table \ref{tab:yields} reports the integrated SN Ia rate or total number of SNe Ia per unit mass of star formation,
\begin{equation}
    \frac{N_{\rm Ia}}{M_\star} = \frac{y_{\rm Fe}^{\rm Ia}}{\bar m_{\rm Fe}^{\rm Ia}},
    \label{eq:snia-rate}
\end{equation}
for each yield set, assuming a mean Fe yield per SN Ia of $\overline m_{\rm Fe}^{\rm Ia}=0.7$ M$_\odot$ \citep{mazzali_common_2007,howell_effect_2009}. The rate for the \yZ{1} yield set is slightly higher than the volumetric rate of $N_{\rm Ia}/M_\star=(1.3\pm0.1)\times10^{-3}\,{\rm M}_\odot^{-1}$ reported by \citet{maoz_star_2017}, but is consistent with their measurement of $N_{\rm Ia}/M_\star=(1.6\pm0.3)\times10^{-3}\,{\rm M}_\odot^{-1}$ for field galaxies. The rate for the \yZ{2} yield set is consistent with the measurement of $N_{\rm Ia}/M_\star=(2.2\pm1.0)\times10^{-3}\,{\rm M}_\odot^{-1}$ by \citet{maoz_type-ia_2012}, while the rate for the \yZ{3} yield set is generally higher than literature values.

Unlike CCSNe, SNe Ia populate a broad distribution of delay times between progenitor formation and explosion. The time-dependent SN Ia rate per unit mass of star formation is defined as
\begin{equation}
    R_{\rm Ia}(t) = 
    \begin{cases}
        \frac{N_{\rm Ia}}{M_\star}
        \frac{f_{\rm Ia}(t)}{\int_{t_{\rm Ia}}^{t_{\rm final}} f_{\rm Ia}(t') dt'}, & t \ge t_{\rm Ia} \\
        0 & t < t_{\rm Ia},
    \end{cases}
    \label{eq:dtd-function}
\end{equation}
where $t_{\rm Ia}=40\,{\rm Myr}$ is the minimum SN Ia delay time and $f_{\rm Ia}(t)$ is the un-normalized form of the DTD. Motivated by recent results suggesting that a large fraction of long-delayed SNe Ia improves agreement with the Milky Way's high-$\alpha$ sequence \citep{palicio_analytic_2023,dubay_galactic_2024}, we adopt a wide plateau DTD of the form
\begin{equation}
    \label{eq:plateau-dtd}
    f_{\rm Ia}(t) =
    \begin{cases}
        1, & t < 1\,{\rm Gyr} \\
        (t/1\,{\rm Gyr})^{-1.1}, & t \ge 1\,{\rm Gyr}.
    \end{cases}
\end{equation}
We also explore a simple power-law DTD,
\begin{equation}
    f_{\rm Ia}^{\rm plaw}(t) = (t/1\,\rm{Gyr})^{-1.1}.
    \label{eq:powerlaw-dtd}
\end{equation}
Equation \ref{eq:powerlaw-dtd} is consistent with SN Ia surveys \citep[e.g.,][]{maoz_star_2017} and results in more prompt Fe production.
We discuss the implications of using the power-law DTD in Section \ref{sec:abundance-distributions}.

@@

In this work, we have highlighted a few predictions of the two-infall scenario and compared against trends from large stellar age catalogs. We have explored a wide range of parameter space, but our investigation is not intended to be exhaustive. In this section, we discuss \added{further extensions to the two-infall model as well as other recent evidence of the Galaxy's evolution.}
